Exercise 3: Software Architecture in Practice Case: Beer Web Store

### 2008-03-17 trunk/SAiP/Module1/H3/doc/architecturaldesign.tex
Fixing \c in Facade

\fixme{Answer question 4.3}

>>>>

There are four major structures in Component-and-Connector:

\begin{itemize}
  \item Process or communicating processes.
	\begin{itemize}
	  \item This structure shows the execution path through a system, and is used to give the engineer an understand about the dynamic behaviour of the system. These structures may help engineers increase Performance and Availability.
	\end{itemize}
  \item Concurrency.
	\begin{itemize}
	  \item This structure is used to see the parallelism in the system, or part of the system, and when a system, or part of a system, is build around this structure it promotes performance. 
	\end{itemize}
  \item Shared data or Repository
	\begin{itemize}
	  \item This is a very good structure to use to illustrate how the data is processed and consumed to/from the database (Server to/from Database Fa\c cade). When a system, or part of a system, is build around this structure it promotes performance and data integrity. 
	\end{itemize}
  \item Client-server
	\begin{itemize}
  		\item This is a very good structure to see the protocols used between the Clients and the Server, and the messages they communicate. When a system, or part of a system, is build around this structure it promotes separation of concern (i.e. Modifiability) and allows for Availability tactics like Load balancing.
	\end{itemize}
\end{itemize}

In the Beer Web Store has two clear C\&C structures, the Shared data structure between the Server and the Database Fa\c cade and the Client-server between the Client and Server (see Figure \ref{fig:module_view}).

The Process or Communicating processes is a more fine-grained structure, and an example of this may be seen in Figure \ref{fig:ad_sequence}.

The Concurrency structure is not used in the overall elements, yet may be employed in a given element to achieve more performance.

\fixme{Possible extension - insert diagrams}

### 2008-03-17 trunk/SAiP/Module1/H3/doc/qualityattributes.tex
Fixing \c in Facade

Instead of creating a web-server which access a database through a specific fa\c ade, one may argue whether the desired functionality may not be generalised. "Look-up in database". This may easily be hidden behind a standardised service, e.g. a web-service, meaning that anyone on the WWW who supplies a database service may be used to host the beer database, and if one becomes dissatisfied with the database provider, it is transparent to simply switch to another.

>>>>

Instead of creating a web-server which access a database through a specific fa\c cade, one may argue whether the desired functionality may not be generalised. "Look-up in database". This may easily be hidden behind a standardised service, e.g. a web-service, meaning that anyone on the WWW who supplies a database service may be used to host the beer database, and if one becomes dissatisfied with the database provider, it is transparent to simply switch to another.
